\documentclass[a4paper]{article}
\usepackage{../../remarks}

\title{"Introduction to Smooth Manifolds": Excercises and Notes}
\author{Chan Kha Vu}
\date{}

\begin{document}

\maketitle
\begin{abstract}
\textit{
    Hey, I'm Vu. This is just a place where I keep all of my notes while reading
    the book \href{https://www.springer.com/gp/book/9780387217529}{"John M. Lee: Introduction to Smooth Manifolds"}.
    I'm an old noob with very weak formal training in Mathematics, so lots of proofs here
    might look messy, too obvious and can be ommited, or even unstrict. Would be very
    grateful if you pointed them out to me tho.
    By the way, you can find more about me on my blog \href{https://hav4ik.github.io}{hav4ik.github.io}.
}
\end{abstract}


\section{Smooth Manifolds}
\bigskip

\begin{exercise}[1-1]
    We denote the equiv. class of $(x, 1)$ and $(x, -1)$ for $x \ne 0$ as $[x]$.
    Each point $x \in M$ has a n-hood $\{ [x+o] \}_{x-r}^{x+r}$ that is
    obviously euclidean by $(x, y) \equiv x$. The second countability follows trivially.
    It is not hausdorff because $0_a$ and $0_b$ cannot be separated by any
    neighbourhoods.
\end{exercise}

\begin{exercise}[1-2]
    Let $M = \bigcup_I M_{i\in I}$ where each $M_i$ is congruent to $\mathbb{R}$,
    then for each $x \in M_i$, it is locally euclidean and, since all $M_i$
    are disjoint, is also hausdorff. It is not second-countable as any base
    would be uncountable.
\end{exercise}

\begin{exercise}[1-3]
    $(\implies)$ By lemma 1.10, each manifold $M$ has a countable basis of precompact
    coordinate balls, so it is a countable union of compact subspaces
    ($\sigma$-compact).

    $( \impliedby )$ It suffices to show $X$ the space is second countable.
    Let $K_n$ be the covering of $X$ by compact sets, and assume they're
    all nonempty. For each $x\in K_n$, there is an open neighborhood
    $U_{x,n}$ which is homeomorphic to an open ball in $\mathbb{R}^m$.
    Then we have $K_n\subset \bigcup_{x\in K_n} U_{x,n}$. By compactness,
    there are finitely many $U_{x,n}$ which cover each $K_n$. By unioning these
    all together for each $n$ gives us a countable covering for $X$ by open sets
    which are homeomorphic to open balls in $\mathbb{R}^m$. Each of these sets
    has a countable basis. The countable union of these sets is also a countable
    set, so it remains to show that this set is a basis, which is easy.
\end{exercise}

\begin{exercise}[1-4]
\begin{enumerate}[label=(\alph*)]
    \item Since $\mathcal{U}$ is a cover of $M$, for each $x\in M$, there is an
        open n-hood $U_x \in \mathcal{U}$ that contains $x$. Since it intersects
        finitely many others, $\mathcal{U}$ is locally finite.
    \item Let's cover $\mathbb{R}^2$ with open sets
        $\left\{ V \right\} \cup \left\{ H_n \right\}_{n\in \mathbb{Z}}$, where
        $H_n = \left\{ (x, y) \mid n - \epsilon < y < n + \epsilon \right\}$,
        $\epsilon < \frac{1}{2}$, and
        $V = \left\{ (x, y) \mid - \epsilon < x < + \epsilon \right\}$.
        Such cover would be locally-finite, but $V$ actually intersects with
        infinitely many other subsets from collection $\mathcal{U}$.
    \item If each $U \in \mathcal{U}$ is precompact, then $\overline{U}$ is
        compact in $M$. For each $x \in \overline{U}$, let $V_x$ be the open
        n-hood of $x$ that intersects with finitely many elements from
        $\mathcal{U}$ (local finity). Since $\overline{U}$ is compact, from the
        cover $\left\{ V_x \right\}_{x \in \overline{U}}$ we can choose a finite
        subcover $V_{x^*}$, each element of which intersects with finite number
        of elements of $\mathcal{U}$. Then, since they all are finite cover of
        $U$, the element $U$ itself intersects with finitely many others from
        $\mathcal{U}$. Q.E.D.
\end{enumerate}
\end{exercise}

\begin{exercise}[1-5]
    $(\impliedby)$ By definition then, $M$ is a topological manifold, thus
    by proposition 1.15 it is paracompact and by proposition 1.11 it has
    countably many connected components.

    $(\implies)$ Let's examine a single connected component $M_0$ of $M$.
    Let $\left\{ (U_x, \phi_x) \right\}$ be the open cover of $M_0$ by open nbrh
    homeomorphic to $\mathbb{R}^n$. For each $U_x$, there is a countable
    basis of precompact coordinate balls, let's call it $\mathcal{B}_{U_x}$. The
    collection of such bases also forms a base $\mathcal{B}$ of topology of
    $M_0$. By paracompactness of $M_0$, $\mathcal{B}$ admits a locally-finite
    refinement, let's call it $\mathcal{B}'$, the elements of which are also
    precompact and forms a new cover of $M_0$.

    Since $M_0$ is locally-euclidean and connected, it is path-connected.
    For arbitrary pair $x, y \in M_0$ let's consider a path
    $\gamma \colon [0, 1] \to M_0$ where $\gamma(0) = x$ and $\gamma(1) = y$.
    Since $[0,1]$ is compact, codomain of $\gamma$ is also compact. So it can be
    covered with finite number of basis elements (precompact coord balls).
    Let's say $\delta(x,y) \in \mathbb{N}$ is the smallest size of all such covers,
    and $\delta(U, V) = \min_{x \in U, y \in V} \delta(x,y)$ for $U, V \in \mathcal{B}'$.
    In other words, from each element of $M_0$, we can reach another elements
    in a finite number of "hops".

    Let's fix an element $V_0 \in \mathcal{B}'$ and denote $\mathbb{V}_n$ as set
    of all $U \in \mathcal{B}' \colon \delta(U, V_0) = n$. It is easy to prove
    that $\mathcal{V}_n$ is finite $\forall n \in \mathbb{N}$. Then the collection
    $\mathcal{B}' = \left\{ \mathcal{V}_n \right\}_{n \in \mathbb{N}}$ is countable.
    Now, since $\mathcal{B}'$ is a refinement of $\mathcal{B}$, $M_0$ is
    second countable.

    Now, as the number of connected components of $M$ is countable, and each
    admits a countable base, the base of whole $M$ is also countable. (Q.E.D)
\end{exercise}

\begin{exercise}[1-6]
    First, let's follow the problem's hint and prove the following lemma:
    \begin{lemma}
        $F_s \colon \mathbb{R}^n \to \mathbb{R}^n$,
        $F_s(x) = \left\| x \right\|^{s-1} x$ where $s>0$ is a homeomorphism but not a diffeomorphism
        unless $s=1$.
    \end{lemma}
    \begin{prf}
        $F_s$ sends each vector $x \in \mathbb{R}^n$ to a $x'$ that has
        the same direction as $x$ and $\left\| x' \right\| = \left\| x \right\|^s$, making
        it a bijection and, since it is clearly continuous, it is a homeomorphism.
        Either $F_s$ or the inverse $F_s^{-1} (x) = \left\| x \right\|^{\frac{1}{s} - 1} x$
        are not smooth at $x=0$ when $s \ne 1$. So $F_s$ is not a diffeomorphism.
        Moreover, $F_s \circ F_{s'}^{-1} = \left\| x \right\|^{\frac{s}{s'} - 1} x$ is not smooth, 
        unless $s' = s$.
    \end{prf}

    Let's get back to our problem. Let's assume $M$ has a smooth structure $\mathcal{A}_0$.
    From $\mathcal{A}_0$, we extract a paracompact cover of coordinate balls from its base,
    which forms a smooth atlas $\mathcal{A}'_0$. Let's consider all $(U, \varphi) \in \mathcal{A}'_0$
    such that $\exists p \in U \colon \varphi(p) = 0$ and $\forall (U', \varphi') \colon U\cap U' = \varnothing$.
    If there are none, we can manually construct one, as we will show later.
    By replacing such charts with $(U, F_s \circ \varphi)$, together with all
    other non-centered charts, we can form an smooth atlas $\mathcal{A}'_s$
    (it is an atlas because $F_s$ is a diffeomorphism on $\mathbb{R}^n \setminus \{0\}$),
    that is not smoothly compatible with $\mathcal{A}'_0$ because $F_s \circ \varphi \circ \psi^{-1} $ is not smooth, unless $s=1$.
    By proposition 1.17, $\mathcal{A}'_0$ belongs to a different smooth structure,
    let's call it $\mathcal{A}_s$. Similarly, we can prove that for any $s>0$ and $s'>0$
    that are not equal to $1$, the transitions $F_s \circ \varphi \circ \varphi^{-1} \circ F_{s'}^{-1} = F_s \circ F_{s'}^{-1} $
    is not smooth, so $\forall s,s'>0 \colon s \ne s'$, $\mathcal{A}_s$ and
    $\mathcal{A}_{s'}$ are not smoothly compatible, thus belongs to different
    smooth structures. Clearly, their number is uncountable.

    Let's show that we can construct an atlas that contains charts centered at
    zero and the center of such charts does not contain in any other charts.
    Get an arbitrary $(U, \varphi)$,
    get an paracompact element $V$ from the local basis such that $\overline{V} \subset U$.
    Since it is closed, $M \setminus \overline{V}$ is open, so is its intersection
    with all other basis elements. The induced topology on $M \setminus \overline{V}$,
    together with the chosen $(U, \varphi)$, forms an atlas smoothly compatible
    with $\mathcal{A}$, which we will also call $\mathcal{A}'_0$. (Q.E.D).
\end{exercise}

\begin{exercise}[1-7]
(a) and (b) are trivial trigonometry, so I wouldn't prove them here.
\begin{enumerate}[topsep=0pt]
    \item[(c)] On charts $\mathbb{S}^n \setminus \{N\}$ and $\mathbb{S}^n \setminus \{S\}$,
        the transition map $\widetilde{\sigma} \circ \sigma^{-1} = -\sigma \circ -\boldsymbol{1} \circ \sigma$
        sends each point $(x_1, \ldots, x_n, x_{n+1})$ to $(x_1, \ldots, x_n, -x_{n+1})$ (mirror symmetry),
        which is a diffeomorphism. It covers $\mathbb{S}^n$, so it is an atlas.
        This atlas defines a unique smooth structure, according to proposition 1.17.
    \item[(d)] It is sufficient to show that $(\mathbb{S}^n \setminus \{N\}, \sigma)$ and
        the chart $\varphi_{i}(x) = (x_1, \dots, x_{i-1}, x_{i+1}, \dots, x_n)$
        are smoothly compatible. In fact, $\sigma \circ \varphi_i^{-1} $ and
        $\varphi_i \circ \sigma^{-1} $ are just reprojections, which are smooth.
\end{enumerate}
\end{exercise}

\begin{exercise}[1-11]
    $M = \overline{\mathbb{B}}^n = \mathbb{B}^n \cup \mathbb{S}^{n-1}$. Hausdorffness
    and second countability follows naturally as $M \in \mathbb{R}^n$. Now every
    point $x \in \mathbb{B}^n$ admits an open nbh $U_x = \mathcal{B}_{1-\|x\|}(x)$
    --- a precompact n-ball that contained in $\mathbb{B}^n$. We pair each such
    nbhs with a natural homeomorphism $\varphi_x \doteq \boldsymbol{1}$ (which
    will be our inner chart).
    For each $x \in \partial\overline{\mathbb{B}}^n = \mathbb{S}^{n-1}$, we construct a chart
    $(U_x, \varphi_x)$ as following. $U_x = \mathcal{B}_{\epsilon}(x) \cap \overline{\mathbb{B}}^n$,
    with $\epsilon$ chosen such that it is much smaller than the hemishpere (precompact coordinate ball in the basis of induced topology).
    We then choose $\varphi_x = \pi_{\overline{\mathbb{HS}}^{n} \mid \mathbb{H}^n} \circ \pi_{\overline{\mathbb{B}}^n \mid \overline{\mathbb{HS}}^n}$.
    Geometrically, $\pi_{\overline{\mathbb{B}}^n \mid \overline{\mathbb{HS}}^n}$ projects
    our nbh $U_x \subseteq \overline{\mathbb{B}}^n$ to a closed unit hemisphere in higher dimension
    (upwards vertically). Then, $\pi_{\overline{\mathbb{HS}}^{n} \mid \mathbb{H}^n}$
    projects that surface horizontally back to $\mathbb{H}^n$. Proving that this
    combination is a diffeomorphism $U_x \to \mathbb{H}^n$ is trivial. From this,
    it follows that our chart is a boundary one. Transition maps between internal
    charts is $\boldsymbol{1}$, which makes our interior atlas smoothly compatible
    with standard structure. Transition map between boundary charts $V$ and $V'$
    are just a combination of diffeomorphic projections, which itself is diffeomorphism.
    Transition maps between interior chart and boundary are also identity maps
    and diffeomorphic projections. So, Our smooth atlas is compatible with standard one.
\end{exercise}

\begin{exercise}[1-12]
    By example 1.8, the product of manifolds is also a manifold of dimension
    equal to the sum of dimensions of these manifolds. So, let $M = M_1 \times \dots \times M_k$
    be a $n = \sum_{i=1}^k n_i$ dimensional manifold, where $n_i$ is the dimensionality
    of $M_i$. Then, we can treat the problem as showing $M \times N$ is a manifold with
    boundary. $M \times N = M\times \text{Int}N \cup M\times \partial N$. Now,
    $M \times \text{Int}N$ is a $n\times m$ manifold ($m$ is the dimensionality of $N$).
    The boundary $M \times \partial N$ is a manifold with boundary with dimension
    $n \times (m-1)$.

    Let's show that each point $x \in M\times \partial N$ is a boundary point.
    Consider a chart $U_x = U^M_x \times U^N_x$. By definition, $U^N_x$ is a
    boundary chart of N, so it is homeomorphic to $\mathbb{H}^m$. Then $U_x$ is
    homeomorphic to $\mathbb{R}^n \times \mathbb{H}^m = \mathbb{H}^{n+m}$. Thus,
    by proposition 1.37, $M \times \partial N$ is the boundary of $M \times N$. (Q.E.D)
\end{exercise}




\section{Smooth Functions and Smooth Maps}

\begin{note}[on ex. 2.1]
    This one is obvious but I'm noob, so I'll state it clear. We need to prove that $C^\infty(M)$ forms a commutative ring, and is a commutative
    and associative algebra over $\mathbb{R}$. The addition $f+g$ satisfies
    axioms of abelian group (namely \textit{closure, associativity, commutativity,
    additive identity}, and \textit{additive inverse}), and the pointwise multiplication
    $f \cdot g$ satisfies monoidal axioms (namely \textit{associativity} and
    \textit{multiplication identity}). The pointwise  \textit{left-} and
    \textit{right-distributivity} of multiplication with respect to addition are also
    satisfied. Thus, $C^\infty(M)$ is a commutative ring. The pointwise multiplication
    is also \textit{bilinear}, together with other properties of the product
    makes $C^\infty(M)$ a associative and commutative algebra.
\end{note}

\begin{note}[on ex. 2.3]
    By $f$ is smooth $\implies$ for every point $p$ there exists a chart $(U, \varphi)$,
    such that $p \in U$ and $ f|_U \circ \varphi^{-1}$ is smooth. This would be
    true for some cover $\mathcal{A}$ of $M$. Let's assume that $(V, \psi)$ does not belong to this cover.
    Then, since we're talking about smooth manifolds, $(V, \psi)$ belongs to the
    same smooth structure, so
    $\forall (U, \varphi) \in \mathcal{A}, U \cap V \ne \varnothing \colon f|_{V\cap U} = f \circ \psi^{-1} = (f \circ \varphi^{-1}) \circ (\varphi \circ \psi^{-1})$.
    Clearly, it is smooth.
\end{note}

\begin{note}[on ex. 2.7]
    First, let's prove the proposition 2.5.
    \begin{itemize}[topsep=0pt]
        \item[(a)] $\implies$ By proposition 2.4, $F$ is continuous, so $F^{-1} (V)$ is open in $M$,
            thus in $U \cap F^{-1} \left( V \right) $. The composite map is
            smooth by definition.

        $\impliedby$ $F\mid_{U \cap F^{-1} (V)} = \varphi \circ \left( \psi \circ F \circ \varphi^{-1} \right) \circ \psi^{-1}$
            is smooth by definition. So, at least on a refinement of charts
            $(U, \varphi)$ and $(V, \psi)$, which are also smooth charts, $F$ is smooth.

        \item[(b)] $\implies$ Applying (a) to every points and every pair of charts
            $U_\alpha$ and $V_\beta$ that nontrivially intersects the image $F(U_\alpha)$,
            we get a formulation of (b). The other way ($\impliedby$) is obvious,
            since it implies (a).
    \end{itemize}
    Proposition 2.6 is quite trivial, and can be implied just by definitions.
\end{note}

\begin{note}[on ex. 2.16]
\begin{enumerate}
    \item[(a)] I suggest this one is actually about diffeomorphisms between manifolds
        $M \xrightarrow[]{f} N \xrightarrow[]{g} K$. Using proposition 2.10 (d),
        $g\circ f$ is smooth and, since their inverse are smooth,
        $f^{-1}\circ g^{-1}$ is also smooth, hence their combination
        is a diffeomorphism.
    \item[(b)] This one is actually about set product, not pointwise product
        (which makes no sense since points of manifold may not equipped with multiplication).
        Having diffeomorphisms $f_1\colon M_1 \to N_1$ and $f_2\colon M_2 \to N_2$,
        we need to show that $f_1 \times f_2$ is also a diffeomorphism.

        Well, the problem is, I skipped lots of calculus class, so I don't know
        of any theorems on products of smooth functions. Let's quickly
        prove the following:

        \begin{lemma}
            for smooth $F_1\colon \mathbb{R}^{n_1} \to \mathbb{R}^{m_1}$ and
            $F_2\colon \mathbb{R}^{n_2} \to \mathbb{R}^{m_2} $ their product is also
            smooth. 
        \end{lemma}
        \begin{prf}
            Let's look at the Jacobian of $F_1 \times F_2$:
            $$
            \begin{pmatrix}
                \left[ \frac{\partial F_1^k}{\partial x_i} \right]_{i \le n_1}^{k \le m_1} & 0 \\
                0 & \left[ \frac{\partial F_2^k}{\partial x_i} \right]_{i>m_1}^{k>m_1}  
            \end{pmatrix} 
            $$
            Clearly, all elements of this matrix are continuous, so $F_1\times F_2 \in C^1 $.
            Now, we need to show that its higher-order partial derivatives are also continuous.
            Clearly:
            $\frac{\partial }{\partial x_j} \left( \frac{\partial F_1^k}{\partial x_i} \right)  $
            is $0$ if $j > n_1$, and continuous otherwise since $F_1$ is smooth. So the shape of higher-order
            partial derivatives will be similar to the Jacobian (blocks of continuous
            functions and zeros on parts that are not in the domain of either $F_1$ or $F_2$).
            This roughly proves that the set product of smooth functions are smooth.
        \end{prf}
            Now, back to the exercise. The map $f_1\times f_2$ are smooth since their coordinate
        representation are smooth as product of smooth functions. Same for their inverse
        $f_1^{-1} \times f_2^{-1}$.

    \end{enumerate}
    The rest is trivial. (c) follows by the fact that continuity of $f$
    and $f^{-1}$ implies openess. (d) is a consequence of (c), and (e) follows
    naturally from (a).
\end{note}

\begin{note}[on ex. 2.24]
    Instead of using proposition 1.15, we follow prop. 1.40 (c) to extract a finite
    refinement. Instead of constructing a basis from only coordinate balls, we need
    to include coordinate half-balls also. The bump function $f_i$ also needs to be
    modified for the case of half-balls.
\end{note}

\begin{note}[on ex. 2.27]
    When $M \equiv \mathbb{R}$, $\varphi \equiv \iota$ (inclusion map),
    $f(x) = \frac{1}{x}$, and $A = (0, \infty)$ is an open set. Clearly, $f$ does
    not have an extension but is smooth on $A$.
\end{note}

\begin{exercise}[2-1]
    $f$ is smooth on $\mathbb{R} \setminus \{0\}$. Let's take $x=0$ and the chart
    on $(U=(-1,1),\varphi=\iota)$ for the domain and $(V=(1-\epsilon, 1+\epsilon), \psi=\iota)$ for
    the codomain, where $\iota$ is the inclusion map. Then, $f^{-1}(V) = [0, +\infty)$
    and $U \cap f^{-1}(V) = [0, 1)$. $\varphi(U \cap f^{-1}(V)) = [0,1)$, so
    clearly $\psi \circ f \circ \varphi^{-1}$ is smooth, but $f$ is not even
    continuous.
\end{exercise}

\begin{exercise}[2-2]
    I just realised that we don't have a lemma that ensures smoothness of projections.
    So, let's just do that!

    \begin{lemma}
        If $M_1 \dots M_{k-1} $ are smooth manifolds without boundary, and $M_k$ is a
        manifold with boundary, then the projection $\pi_i \colon M_1 \times M_2 \times \dots \times M_k \to M_i$
        is smooth.
    \end{lemma}
    \begin{prf}
        Here I need to point out that, by proposition 1.45, the product is a
        manifold with boundary if there are at most one manifold with boundary.
        Product of multiple manifolds with boundary is not a manifold with boundary
        (see the notes on proposition 1.45).
        Consider charts $(U, \varphi) = (U_1 \times \dots \times U_k, \varphi_1 \times \dots \times \varphi_k)$,
        where $(U_i, \varphi_i)$ are smooth charts of $i$-th manifold.
        Then, $\pi_i = \varphi_i \circ \pi_i \circ \varphi^{-1}$ is smooth, as a
        mapping from $\mathbb{R}^{n_1} \times \dots \times \mathbb{R}^{n_k}$ to $\mathbb{R}^{n_i} $,
        we have already proven before that it is smooth.
    \end{prf}

    Now, let's get back to the original problem. The $\implies $ case is obvious,
    since by proposition 2.10 (d), composition of smooth $F$ and smooth $\pi_i$
    is also a smooth map. Let's prove the $\impliedby$ case, i.e. if $F_i$ is 
    smooth then $F$ is smooth.
\end{exercise}

\begin{exercise}[2-3]
  \begin{enumerate}
    \item[(a)]
      For education purpose, let's choose the stereographic projection
      $\sigma \colon \mathbb{S}^1 \setminus \{N\} \to \mathbb{R}^1$, the
      properties of which has been discussed in exercise (1-7), defined in
      complex coordinates as:
      $$
      \sigma(e^{i\theta} ) = \frac{\cos\theta}{1-\sin\theta }
      \quad \text{and} \quad
      \sigma^{-1}(u) = \frac{2u + i(u^2-1)}{u^2+1}
      $$
      And we can define the projection $\widetilde{\sigma}$ from the south pool,
      together with $\widetilde{\sigma}^{-1}$, that can be expressed similarly as:
      $$
      \widetilde{\sigma}(e^{i\theta} ) = \frac{\cos\theta}{1+\sin\theta }
      \quad \text{and} \quad
      \widetilde{\sigma}^{-1}(u) = \frac{2u - i(u^2-1)}{u^2+1}
      $$
      The n-th power map can be expressed
      in complex coordinates:
      $$
      p_n(\cos\theta + i\sin\theta) = \cos(n\theta) + i\sin(n\theta)
      $$
      The coordinate representation $\widehat{p_n} = \psi \circ p_n \circ \varphi^{-1}$,
      where $\psi$ and $\varphi$ are both either $\sigma$ or $\widetilde{\sigma}$.
      Choosing the right chart for each point, one can express $\widehat{p_n}$ as follows:
      \begin{align*}
        \widehat{p_n}(u) &= \psi \circ p_n \circ \varphi^{-1}(u) =
        \left| \cos\phi = \frac{2u}{u^2+1}, \sin\phi = \frac{\pm (u^2-1)}{u^2+1}\right|
        \\&=
        \psi \circ p_n (\cos\phi + i\sin\phi) = \psi(\cos(n\phi) + i\sin(n\phi))
        \\&=
        \frac{\cos(n\phi)}{1 \pm \sin(n\phi)} = 
        \frac{\cos\left(n\left( \arccos\left( \frac{2u}{u^2+1} \right)  \right)\right) }
        {1 \pm \sin\left(n\left( \arccos\left( \frac{2u}{u^2+1} \right) \right) \right)}
      \end{align*}
      Which is smooth if codomain is a domain of $\arccos$. Obviously, we can cover
      each point of $\mathbb{R}$ with a collection of such codomains (just got lazy at this point lol).

    \item[(b)] Again, we will use stereographic projections, just because we can:
      $$
      \sigma_\pm (x^1,\dots ,x^{n+1} ) = \frac{(x^1,\dots ,x^n)}{1\mp x^{n+1} },
      \quad\text{and}\quad
      \sigma_\pm ^{-1}(u^1,\dots ,u^n) =\pm \frac{(2u^1,\dots ,2u^n,|u|^2-1)}{|u|^2+1}
      $$
      Let's consider the coordinate representation $\widehat{\alpha} = \sigma_\mp \circ \alpha \circ \sigma_\pm ^{-1}$.
      It is wel defined on all of $\mathbb{R}^n$ since ... well ... it's obvious.
      Then, the following is smooth (similarty we can prove for $\widehat{\alpha}_-$):
      \begin{align*}
        \widehat{\alpha}_+(u^1,\dots ,u^n) &= \sigma_- \left( - \frac{(2u^1,\dots ,2u^n,|u|^2-1)}{|u|^2+1}\right)
        \\&=
        -\frac{(2u^1,\dots ,2u^n)}{|u|^2+1} \left( 1 - \frac{|u|^2-1}{|u|^2+1} \right) ^{-1}
        \\&=
        -\frac{(2u^1,\dots ,2u^n)}{|u|^2+1} \frac{|u|^2+1}{2} = -(u^1,\dots ,u^n)
      \end{align*}
  \end{enumerate}
\end{exercise}

\begin{exercise}[2-5 (b)]
  $(\implies)$ First, let's show that if $f \circ \psi^{-1}\colon \widetilde{\mathbb{R}}\to \mathbb{R}$ is smooth, 
  where $\psi^{-1}(x) = x^{\frac{1}{3}} $, then $f^{(n)} (0) = 0$ for all $n \nmid 3$.
  We can express $f = (f \circ \psi^{-1}) \circ \psi$, and apply the combinatorial
  form of the \href{https://en.wikipedia.org/wiki/Fa%C3%A0_di_Bruno%27s_formula}{Faà di Bruno's formula}
  to express the $n$-th derivative:
  $$
  \frac{d ^n}{d x^n} (\varphi \circ \psi) (x)=
  \sum_{\pi \in \Pi}
    \frac{d^{|\pi|} \varphi}{d x^{|\pi|} }  \left( \psi(x) \right) \cdot
    \prod_{B \in \pi} \frac{d^{|B|} \psi}{d x^{|B|} } (x)\,,
  $$
  where $\varphi = f \circ \psi^{-1}$, $\pi$ runs throught $\Pi$, which is the
  collection of all partitions of the set $\{i\}_{i=1}^n$, and $B$ runs through
  all blocks of partition $\pi$. The values of $\psi^{(n)} (0)$ are all $0$, except
  for $n = 3$. So, the product is positive only if $|B| = 3$ for all $B \in \pi$.
  It follows that the formula above can only give non-zero values if $n$ is divisible
  by $3$.

  $(\impliedby)$ Now, assuming that $f^{(n)} (0) = 0$ for all $n \nmid 3$, we need to prove that
  $\varphi = f \circ \psi^{-1}$ is smooth. For all $x \ne 0$, $\psi^{-1}$ is smooth,
  so $\varphi$ is smooth there as well. The problem place is $0$. Let's expand $f$
  into Taylor's series:
  $$
  f(x) = \sum_{k=0}^n \frac{f^{(k)}(0)}{k!} x^k + R_n(x)
  $$
  Since $f$ is smooth, thus absolutely continuous, we can use the integral form
  of the remainder $R_n$:
  $$
  R_n(x) = \int_{0}^x \frac{(x-t)^n}{n!} f^{(n+1)}(t) dt= x^{n+1} \int_0^1\frac{(1-t)^n}{n!}f^{(n+1)}(x t)dt= x^{n+1} g_{n+1}(x)
  $$
  with $g_{n+1} $ obviously smooth. Taking $n = 3m$, we get:
  $$
  f \circ \psi^{-1}(x) = f(\sqrt[3]{x}) = \sum_{k=0}^m a_k x^k + x^{m+\frac{1}{3}}g_{3m+1}(\sqrt[3]{x})
  $$
  where $a_k$ are some constants. Now, let's prove by induction that if $h$ is of class $C^m$, then
  $x^{m+\frac{1}{3}} h\left(\sqrt[3]{x}\right)$ is also of class $C^m$.
  For $m=0$, it is clear (product of continuous is continuous). Assume it is true
  for $m-1$. The derivative of $x^{m+\frac{1}{3}} h(\sqrt[3]{x}) $ for $x\ne 0$ is:
  $$
  x^{(m-1) +\frac{1}{3}} \left(\frac{1}{3}h'\left( \sqrt[3]{x} \right)  + \left( m+\frac{1}{3} \right) h \left( \sqrt[3]{x} \right)  \right )
  $$
  The limit at $0$ is $0$ --- we have a finite limit in the bracket, multiplied by some x to a positive power.
  The derivative can be extended at $0$ by the extension lemma. So, the derivative
  is of class $C^{m-1}$, which makes $x^{m+\frac{1}{3}} h\left(\sqrt[3]{x}\right)$
  be of class $C^m$.

  Substituting $h$ with the smooth $g_{3m+1} $, we have proven that $f \circ \psi^{-1}$
  is a smooth function, making $f$ a smooth mapping between $\widetilde{\mathbb{R}}$
  and $\mathbb{R}$.
\end{exercise}

\begin{exercise}[2-7]
  Let's show that for any $k \in \mathbb{N}$, there is a collection $\{f_i\}_{i=1}^k$
  of linearly independent functions. First, we will construct such collection of 
  functions with disjoint support.

  Choose a coordinate cube $U \subset M$ and a homeomorphism $\varphi \colon U \to (0,1)^n$.
  For each $i = 1, \dots ,k$, let $B_i = (0,1)^{n-1} \times (\frac{i-1}{k}, \frac{i}{k})$.
  Inside each $B_i$, let $A_i$ be a nonempty closed set. By propositoin 2.25,
  there exists a smooth bump function $f_i$ for $A_i$ supported in $B_i$.

  Obviously, since the supports are all distinct, then $f_i$ cannot be expressed
  as a linear combination of other $f_j \colon j \ne i$, because they will be
  all zero on $\supp f_i$.
\end{exercise}




\section{Some endnote}

Just found \href{https://wj32.org/wp/wp-content/uploads/2012/12/Introduction-to-Smooth-Manifolds.pdf}{this guy}
that, surprisingly, also writes up the exercies in a nice document!
I'm not the only crazy one :D His notes are not so messy and filled with re-proving
obvious things as mine though.

\end{document}
